Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2016-10-01 paper.tex
Rev 2 comments up through p3

There are many examples in the literature of 2-D cross-flow turbine simulations
with widely varying results. Balduzzi et al.~\cite{Balduzzi2016} provides
a summary of recent efforts and an attempt to standardize a methodology for
using Reynolds-averaged Navier--Stokes (RANS) to correctly predict performance
of a 2-D CFT. Howell et al.~\cite{Howell2010}, performed both 2-D and 3-D
simulations of a high solidity cross-flow turbine using a $k$--$\epsilon$
renormalization group (RNG) turbulence model. The results from the 2-D
simulations over-predicted power coefficient, while the 3-D case matched well
with wind tunnel measurements near the tip speed ratio of maximum power. In
general, 3-D simulations are less common, but have begun to appear more
frequently recently---a testament to the progress towards higher computing
power.

An overview of 3-D blade-resolved cross-flow turbine simulations reported in the
literature is presented in Table~\ref{tab:cfd-refs}. The $k$--$\omega$ SST RANS
turbulence model is shown to be a popular choice due to its success in
predicting flows with adverse pressure gradients and
separation~\cite{Menter2003}. Higher fidelity methods that resolve the large
scales of turbulence, such as large eddy and detached eddy simulation have also
been used. Note that for all the studies listed, model validation was performed
for either performance or wake predictions---not both---and in some case omitted
entirely.

@@

Modeling the boundary layer flows on cross-flow turbine blades is essential to
predicting the blade loading. This flow condition presents a challenge due to
the dynamically changing inflow velocity and angle of attack---which often
exceeds static stall values and causes dynamic stall. Furthermore, the ability
to predict the occurrence and interdependence of boundary layer transition to
turbulence and separation can have dramatic influence on the blade loading and
therefore the predicted turbine power output. These challenges present
significant obstacles to the prospect of using CFD to replace wind tunnel or
tank testing of physical models.

>>>>

There are many examples in the literature of 2-D cross-flow turbine simulations
with widely varying results. Balduzzi et al.~\cite{Balduzzi2016} provides a
summary of recent efforts and an attempt to standardize a methodology for using
Reynolds-averaged Navier--Stokes (RANS) to correctly predict performance of a
2-D CFT. Howell et al.~\cite{Howell2010}, performed both 2-D and 3-D simulations
of a high solidity cross-flow turbine using a $k$--$\epsilon$ renormalization
group (RNG) turbulence model. The results from the 2-D simulations
over-predicted power coefficient since the rotor had a low aspect ratio, while
the 3-D case matched well with wind tunnel measurements near the tip speed ratio
of maximum power. In general, 3-D simulations are less common, but have begun to
appear more frequently recently---a testament to the progress towards higher
computing power.

An overview of 3-D blade-resolved cross-flow turbine simulations reported in the
literature is presented in Table~\ref{tab:cfd-refs}. The $k$--$\omega$ SST RANS
turbulence model is shown to be a popular choice due to its success in
predicting flows with adverse pressure gradients and
separation~\cite{Menter2003}. Higher fidelity methods that resolve the large
scales of turbulence, such as large eddy and detached eddy simulation have also
been used, though the high computational expense of these techniques may
preclude their use in industrial applications. Note that for all the studies
listed, model validation was performed for either performance or wake
predictions---not both---and in some case omitted entirely. In general, the 3-D
RANS results cannot replicate a turbine's entire performance envelope, i.e.,
$C_P$--$\lambda$ curve, but are successful for some tip speed ratios.

@@

Modeling the boundary layer flows on cross-flow turbine blades is essential to
predicting the blade loading. This flow condition presents a challenge since the
blades encounter a constantly changing relative velocity and angle of
attack---which often exceeds static stall values and causes dynamic stall.
Furthermore, the ability to predict the occurrence and interdependence of
boundary layer transition to turbulence and separation can have dramatic
influence on the blade loading and therefore the predicted turbine power output.
These challenges present significant obstacles to the prospect of using CFD to
replace wind tunnel or tank testing of physical models.
